Automatically generated NE tagged corpora for English and Hungarian

### 2012-04-26 paper/engNERwiki.tex
Email address changed to use the official .mta domain.

\author{Dávid Márk Nemeskey \\
  Research Institute for \\ Computer Science and Automation \\
  Hungarian Academy of Sciences \\
  H-1111 Lágymányosi út 11, Budapest \\
  {\tt nemeskey.david@sztaki.hu} \\\And
  Eszter Simon \\
  Research Institute for Linguistics \\
  Hungarian Academy of Sciences \\
  H-1068 Benczúr utca 33, Budapest \\
  {\tt simon.eszter@nytud.mta.hu} \\}

@@

Wikipedia has been applied for several NLP tasks, e.g.~word sense disambiguation, ontology and thesaurus building, and question answering, as Medelyan et al.~\shortcite{Medelyan:09} point out in their fully detailed survey about mining meaning from Wikipedia.

@@

Our goal is to create a large NE annotated corpus, automatically generated from Wikipedia articles. We follow a similar path to Nothman et al.~\shortcite{Nothman:08}, and we broke down the process into four steps:

\begin{enumerate}
\item Classify Wikipedia articles into entity classes.
\item Parse Wikipedia and split articles into sentences.
\item Label NEs according to link targets.
\item Select sentences for inclusion in the corpus.
\end{enumerate}

>>>>

\author{Dávid Márk Nemeskey \\
  Research Institute for \\ Computer Science and Automation \\
  Hungarian Academy of Sciences \\
  H-1111 Lágymányosi út 11, Budapest \\
  {\tt nemeskey.david@sztaki.mta.hu} \\\And
  Eszter Simon \\
  Research Institute for Linguistics \\
  Hungarian Academy of Sciences \\
  H-1068 Benczúr utca 33, Budapest \\
  {\tt simon.eszter@nytud.mta.hu} \\}

@@

Wikipedia has been applied to several NLP tasks, e.g.~word sense disambiguation, ontology and thesaurus building, and question answering, as Medelyan et al.~\shortcite{Medelyan:09} point out in their fully detailed survey about mining meaning from Wikipedia.

@@

Our goal is to create a large NE annotated corpus, automatically generated from Wikipedia articles. We follow a similar path to Nothman et al.~\shortcite{Nothman:08} and we broke down the process into four steps:

\begin{enumerate}
\item Classify Wikipedia articles into entity classes.
\item Parse Wikipedia and split articles into sentences.
\item Label named entities in the text.
\item Select which sentences are included in the corpus.
\end{enumerate}
